Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-21 string_jpam.tex
fixes #14

Solutions to this differential equation correspond to a taut string
confined to Flamm's paraboloid~\cite{flamm1916}; see
Figure~\ref{flamm}.

There does not appear to be a simple analytical solution but
nevertheless we may make several observations.
Equation~\ref{rdashdash} is a second-order nonlinear ordinary
differential equation and thus has two constants of integration.
There are two qualitatively different types of solutions: those with a
tangential point ($r'=0,r>1$), and those without.  Consider first
solutions with such a point: there exists a pair~$\left(r,\phi\right),
r>1$ at which~$r'(\phi)=0$.  This point must be unique,
as~$r''(\phi)>0$, and be the closest approach of the string to the
event horizon.

>>>>

\noindent 
Solutions to equation~\ref{rdashdash} correspond to a taut string
confined to Flamm's paraboloid~\cite{flamm1916}; see
Figure~\ref{flamm}.  It is interesting to compare
equation~\ref{rdashdash} with the corresponding equation for null
geodesics, which is usually given~\cite{wald} in terms of $u=r^{-1}$
as $u''=3u^2/2-u$ but is equivalent
to~$r''\left(\phi\right)=r-\frac{3}{2}+\frac{2r'}{r}$.

There does not appear to be a simple analytical solution to
equation~\ref{rdashdash} but nevertheless we may make several
observations.  Equation~\ref{rdashdash} is a second-order nonlinear
ordinary differential equation and thus has two constants of
integration.  There are two qualitatively different types of
solutions: those with a tangential point ($r'=0,r>1$), and those
without.  Consider first solutions with such a point: there exists a
pair~$\left(r,\phi\right), r>1$ at which~$r'(\phi)=0$.  This point
must be unique, as~$r''(\phi)>0$, and be the closest approach of the
string to the event horizon.
